---
title: "Spiral horned antelope"
author: "Kaitlyn Gaynor"
date: "8/23/2019"
output: 
  html_document:
    theme: cosmo
editor_options:
  chunk_output_type: console
---

### Summary of camera trap data from 2016-2018 for the Tragelaphine antelope

I measured species distribution in two ways:

* RAI = Relative Activity Index. This is a simple measure of the number of independent camera trap detections per trap-night. Even though it is very simple, I kind of think it's the better approach

* Occupancy = a presence/absence measure. This was a multi-species model, in which covariates for each species were drawn from a normally-distributed  community-level hyper-parameter (Rich et al. 2016). I think this is a less meaningful approach for common species, like bushbuck, which are present pretty much everywhere
For more details on both of these, see the methods of my dissertation chapter.

The figures below show the model coefficients for each spatial covariate (for RAI models, I took a model-averaging approach). I showed the same thing in two different ways: the first set of figures facilitate comparison between species; the second, between seasons.

Again, the details of the source data for each covariate are described in the supplementary materials of my dissertation chapter.

Note:
Dry season = December - March
Wet season = July - September


```{r setup, echo = FALSE, message = FALSE}
setwd("~/Dropbox/projects/GORONGOSA2/Camera Trap Grid/R")

library(ggplot2)
library(plyr)
library(rgdal)
library(broom)
library(raster)
library(data.table)
library(forcats)

## Wet1+2 and Dry1+2 all species (with covariates)
# some of this code isn't necessary; just copied over from the analyses of all species

Spp <- read.csv("Data/2018spp_kingdon.csv") # read in species traits

sppcov.wet <- read.csv("Results/Occupancy/033019/Wet_year1and2_withcovariates_species.csv")
names(sppcov.wet) <- c("Factor", "SppCode", "Mean", "SD", "LCI", "UCI")

sppcov.dry <- read.csv("Results/Occupancy/033019/Dry_year1and2_withcovariates_species.csv")
names(sppcov.dry) <- c("Factor", "SppCode", "Mean", "SD", "LCI", "UCI")

# join the model output and trait information
sppcov.wet <- join(sppcov.wet, Spp, by = "SppCode")
sppcov.dry <- join(sppcov.dry, Spp, by = "SppCode")

# add season, and then combine
sppcov.wet$Season <- "wet"
sppcov.dry$Season <- "dry"
sppcov <- rbind(sppcov.wet, sppcov.dry)

# combine lion levels
sppcov$Factor <- fct_collapse(sppcov$Factor, lion = c("lion.dry", "lion.wet"))

# order by body size
sppcov$CommName_Full <- reorder(sppcov$CommName_Full, sppcov$Weight)

# create another factor w/ collapsed diet categories
sppcov$Hempsen_diet2 <- fct_collapse(sppcov$Hempsen_diet, grazer = c("GRO","GRV"), nongrazer = c("BGI", "BRW", "FRG", "GEN"))

# read in RAI results
averaged.results.combined.df2 <- read.csv('Results/RAI/averaged.results.combined.df2.csv')
```

#### Coefficients for all three species, for each season
```{r better plots, echo = FALSE}
ggplot(subset(averaged.results.combined.df2, GenusLatin =="Tragelaphus" & Season == "dry"), aes(x=Covariate, y=Estimate, col = CommName_Full)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "RAI coefficients (dry season)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, GenusLatin =="Tragelaphus" & Season == "dry"), aes(x=Factor, y=Mean, col = CommName_Full)) + 
  geom_errorbar(aes(ymin = LCI, ymax = UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "Occupancy coefficients (dry season)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(averaged.results.combined.df2, GenusLatin =="Tragelaphus" & Season == "wet"), aes(x=Covariate, y=Estimate, col = CommName_Full)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "RAI coefficients (wet season)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, GenusLatin =="Tragelaphus" & Season == "wet"), aes(x=Factor, y=Mean, col = CommName_Full)) + 
  geom_errorbar(aes(ymin = LCI, ymax = UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "Occupancy coefficients (wet season)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")
```

#### Coefficients for each season, for each species
```{r better plots2, echo = FALSE}
ggplot(subset(averaged.results.combined.df2, CommName_Full =="Bushbuck"), aes(x=Covariate, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "RAI coefficients - Bushbuck") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, CommName_Full == "Bushbuck"), aes(x=Factor, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin = LCI, ymax = UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "Occupancy coefficients - Bushbuck") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(averaged.results.combined.df2, CommName_Full =="Nyala"), aes(x=Covariate, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "RAI coefficients - Nyala") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, CommName_Full == "Nyala"), aes(x=Factor, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin = LCI, ymax = UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "Occupancy coefficients - Nyala") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(averaged.results.combined.df2, CommName_Full =="Kudu"), aes(x=Covariate, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "RAI coefficients - Kudu") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, CommName_Full == "Kudu"), aes(x=Factor, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin = LCI, ymax = UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "Occupancy coefficients - Kudu") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")
```

```{r plots, eval = FALSE, echo = FALSE}
# plot covariate effects

## Fire frequency

ggplot(subset(averaged.results.combined.df2, Covariate == "fire.interval" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "Fire frequency & RAI", tag = "A)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, Factor == "fire.interval" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Fire frequency & occupancy", tag = "B)") +
  xlab("Species") +
  ylab("Beta Coefficient")

## Lion density

ggplot(subset(averaged.results.combined.df2, Covariate == "lion" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, space = "free_x", scales = "free_x") +
  labs(title = "Lions & RAI", tag = "A)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, Factor == "lion" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Lions & occupancy", tag = "B)") +
  xlab("Species") +
  ylab("Beta Coefficient")

## Pan density

ggplot(subset(averaged.results.combined.df2, Covariate == "panscon.250m" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Pan density & RAI", tag = "A)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, Factor == "panscon.250m" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Pan density & occupancy", tag = "B)") +
  xlab("Species") +
  ylab("Beta Coefficient")

## Poaching

ggplot(subset(averaged.results.combined.df2, Covariate == "poaching" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Poaching & RAI", tag = "A)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, Factor == "poaching" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Poaching & occupancy", tag = "B)") +
  xlab("Species") +
  ylab("Beta Coefficient")

## Distance to road

ggplot(subset(averaged.results.combined.df2, Covariate == "road.major.distance" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, scales = "free_x", space = "free_x") +
  labs(title = "Roads & RAI", tag = "A)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, Factor == "road.major.distance" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Roads & occupancy", tag = "B)") +
  xlab("Species") +
  ylab("Beta Coefficient")

## Distance to river

ggplot(subset(averaged.results.combined.df2, Covariate == "river.distance" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, scales = "free_x", space = "free_x") +
  labs(title = "Rivers & RAI", tag = "A)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, Factor == "river.distance" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Rivers & occupancy", tag = "B)") +
  xlab("Species") +
  ylab("Beta Coefficient")

## Termite mound density

ggplot(subset(averaged.results.combined.df2, Covariate == "termite.count.100m" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, scales = "free_x", space = "free_x") +
  labs(title = "Termite mound density & RAI", tag = "A)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, Factor == "termite.count.100m" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Termite mound density & occupancy", tag = "B)") +
  xlab("Species") +
  ylab("Beta Coefficient")

## Tree cover

ggplot(subset(averaged.results.combined.df2, Covariate == "tree.hansen" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, scales = "free_x", space = "free_x") +
  labs(title = "Tree cover & RAI", tag = "A)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, Factor == "tree.hansen" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Tree cover & occupancy", tag = "B)") +
  xlab("Species") +
  ylab("Beta Coefficient")

## Distance to Lake Urema

ggplot(subset(averaged.results.combined.df2, Covariate == "urema.distance" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Estimate, col = Season)) + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
#  facet_grid(~Hempsen_category, scales = "free_x", space = "free_x") +
  labs(title = "Lake Urema & RAI", tag = "A)") +
  xlab("Species") +
  ylab("Model-Averaged Coefficient")

ggplot(subset(sppcov, Factor == "urema.distance" & GenusLatin =="Tragelaphus"), aes(x=CommName_Full, y=Mean, col = Season)) + 
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.1, position = position_dodge(width = .75)) +
  geom_point(position = position_dodge(width = .75)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  geom_hline(aes(yintercept = 0), linetype="dashed") +
  labs(title = "Lake Urema & occupancy", tag = "B)") +
  xlab("Species") +
  ylab("Beta Coefficient")
```

#### Mapping model output

Here are maps of Relative Activity Index in the camera trap grid, based on model output.

```{r mapping model output, echo = FALSE}
bushbuck_dry_raster <- raster('bushbuck_dry_raster.tif')
plot(bushbuck_dry_raster, main = "Bushbuck Dry Season")

bushbuck_wet_raster <- raster('bushbuck_wet_raster.tif')
plot(bushbuck_wet_raster, main = "Bushbuck Wet Season")

nyala_dry_raster <- raster('nyala_dry_raster.tif')
plot(nyala_dry_raster, main = "Nyala Dry Season")

nyala_wet_raster <- raster('nyala_wet_raster.tif')
plot(nyala_wet_raster, main = "Nyala Wet Season")

kudu_dry_raster <- raster('kudu_dry_raster.tif')
plot(kudu_dry_raster, main = "Kudu Dry Season")

kudu_wet_raster <- raster('kudu_wet_raster.tif')
plot(kudu_wet_raster, main = "Kudu Wet Season")
```

The wet season kudu map is kind of useless, because none of the covariates in the model were very important.

